Type-safe client-server communication for functional web applications

### 2014-02-28 paper.tex
Add abstract.

\begin{abstract}
This is the text of the abstract.
\end{abstract}

>>>>

\begin{abstract}
Developing web applications, especially applications which need to communicate
with a server, is often a painful experience. What is conceptually a single
monolithic application is forcefully split into a client and a server
explicitly communicating over the network, with all the code duplication,
complexity and lost type safety this entails.

We propose instead a development model in which a web application is written
and compiled as a whole, allowing for synchronous, type safe client-server
communication without the need for explicit networking code, as well as the
sharing of code between client and server.
\end{abstract}
